### 2021-04-13 pldi21/discussion.tex
acks and ccs xml

The authors thank
Pavel Panchekha and 
 anonymous referees at TyDe 2019, POPL 2021 and PLDI 2021  
for thoughtful feedback that has significantly improved this paper. 
This material is based upon work supported by the National Science Foundation 
under Grant No. 1814900 and 1817145.

>>>>

We thank
Pavel Panchekha and  
 anonymous referees at TyDe 2019, POPL 2021 and PLDI 2021  
for thoughtful feedback that has improved this paper. 
This material is based upon work supported by the National Science Foundation 
under Grant No. 1814900 and 1817145.
